R Notebook

### 2023-11-04 R_code/paper_analysis.Rmd
new changes

```{r}
library(scales)
library(tidyverse)
library(caret)
library(ggpubr)
library(pROC)
```

@@

fasttree_all_models_performance = read_tsv(paste(prefix,"/fasttree/all_models_performance.tsv", sep = ""))
fasttree_final_models_performance = read_tsv(paste(prefix,"/fasttree/final_model_performance.tsv", sep = ""))
fasttree_group_performance = read_tsv(paste(prefix,"/fasttree/groups_performance.tsv", sep = ""))
fasttree_vi =  read_tsv(paste(prefix,"/fasttree/model_standard_vi.tsv", sep = ""))
fasttree_enriched_test = read_tsv(paste(prefix,"/fasttree/test_model_standard_enriched.tsv", sep = ""))
#####
iqtree_all_models_performance = read_tsv(paste(prefix,"/iqtree/all_models_performance.tsv", sep = ""))
iqtree_final_models_performance = read_tsv(paste(prefix,"/iqtree/final_model_performance.tsv", sep = ""))
iqtree_group_performance = read_tsv(paste(prefix,"/iqtree/groups_performance.tsv", sep = ""))
iqtree_vi =  read_tsv(paste(prefix,"/iqtree/model_standard_vi.tsv", sep = ""))
iqtree_enriched_test = read_tsv(paste(prefix,"/iqtree/test_model_standard_enriched.tsv", sep = ""))
#####
raxml_all_models_performance = read_tsv(paste(prefix,"/raxml/all_models_performance.tsv", sep = ""))
raxml_final_models_performance = read_tsv(paste(prefix,"/raxml/final_model_performance.tsv", sep = ""))
raxml_group_performance = read_tsv(paste(prefix,"/raxml/groups_performance.tsv", sep = ""))
raxml_vi =  read_tsv(paste(prefix,"/raxml/model_standard_vi.tsv", sep = ""))
raxml_enriched_test = read_tsv(paste(prefix,"/raxml/test_model_standard_enriched.tsv", sep = ""))

@@

Choose specific program
```{r}
program = 'raxml'
if (program=='fasttree') {
    all_models_performance = fasttree_all_models_performance
    final_models_performance = fasttree_final_models_performance
    group_performance = fasttree_group_performance
    vi = fasttree_vi
    enriched_test = fasttree_enriched_test

} else if (program=='iqtree') {
    all_models_performance = iqtree_all_models_performance
    final_models_performance = iqtree_final_models_performance
    group_performance = iqtree_group_performance
    vi = fasttree_vi
    enriched_test = iqtree_enriched_test
} else if (program=='raxml') {
    all_models_performance = raxml_all_models_performance
    final_models_performance = raxml_final_models_performance
    group_performance = raxml_group_performance
    vi = fasttree_vi
    enriched_test = raxml_enriched_test
}
```

@@

>>>>

```{r}
library(scales)
library(tidyverse)
library(caret)
library(ggpubr)
library(pROC)
```
```{r}
validation_data_prefix = "/Users/noa/Workspace/bootstrap_results/validation_data"
fasttree_validation_data = read_tsv(paste(validation_data_prefix,"/simulations_df_fasttree.tsv", sep = ""))
raxml_validation_data = read_tsv(paste(validation_data_prefix,"/simulations_df_raxml.tsv", sep = ""))
iqtree_validation_data = read_tsv(paste(validation_data_prefix,"/simulations_df_iqtree.tsv", sep = ""))
```

@@

fasttree_all_models_performance = read_tsv(paste(prefix,"/fasttree/all_models_performance.tsv", sep = ""))
fasttree_final_models_performance = read_tsv(paste(prefix,"/fasttree/final_model_performance.tsv", sep = ""))
fasttree_group_performance = read_tsv(paste(prefix,"/fasttree/groups_performance.tsv", sep = ""))
fasttree_vi =  read_tsv(paste(prefix,"/fasttree/model_standard_vi.tsv", sep = ""))
fasttree_enriched_test = read_tsv(paste(prefix,"/fasttree/test_model_standard_enriched.tsv", sep = ""))
validation_data_fasttree = 
#####
iqtree_all_models_performance = read_tsv(paste(prefix,"/iqtree/all_models_performance.tsv", sep = ""))
iqtree_final_models_performance = read_tsv(paste(prefix,"/iqtree/final_model_performance.tsv", sep = ""))
iqtree_group_performance = read_tsv(paste(prefix,"/iqtree/groups_performance.tsv", sep = ""))
iqtree_vi =  read_tsv(paste(prefix,"/iqtree/model_standard_vi.tsv", sep = ""))
iqtree_enriched_test = read_tsv(paste(prefix,"/iqtree/test_model_standard_enriched.tsv", sep = ""))
#####
raxml_all_models_performance = read_tsv(paste(prefix,"/raxml/all_models_performance.tsv", sep = ""))
raxml_final_models_performance = read_tsv(paste(prefix,"/raxml/final_model_performance.tsv", sep = ""))
raxml_group_performance = read_tsv(paste(prefix,"/raxml/groups_performance.tsv", sep = ""))
raxml_vi =  read_tsv(paste(prefix,"/raxml/model_standard_vi.tsv", sep = ""))
raxml_enriched_test = read_tsv(paste(prefix,"/raxml/test_model_standard_enriched.tsv", sep = ""))

@@

Choose specific program
```{r}
program = 'fasttree'
if (program=='fasttree') {
    all_models_performance = fasttree_all_models_performance
    final_models_performance = fasttree_final_models_performance
    group_performance = fasttree_group_performance
    vi = fasttree_vi
    enriched_test = fasttree_enriched_test
    validation_data = fasttree_validation_data

} else if (program=='iqtree') {
    all_models_performance = iqtree_all_models_performance
    final_models_performance = iqtree_final_models_performance
    group_performance = iqtree_group_performance
    vi = fasttree_vi
    enriched_test = iqtree_enriched_test
    validation_data = iqtree_validation_data
} else if (program=='raxml') {
    all_models_performance = raxml_all_models_performance
    final_models_performance = raxml_final_models_performance
    group_performance = raxml_group_performance
    vi = fasttree_vi
    enriched_test = raxml_enriched_test
    validation_data = raxnk_validation_data
}
```

@@

```
Validation_data
```{r}
validation_data
```
